Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-10 draft/accordionComplexSurfaces.tex
strings

The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.

\begin{definition}
\label{def:string}
Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
A \defn{finite string} for~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{itemize}
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{itemize}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
We note that there is only one string of length 
%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
%We usually denote strings by~$\rho, \sigma, \tau$.

%We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
%\(
%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}
%\)
%the set of \defn{almost positive unoriented strings}.
%Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.
%\end{enumerate}
\end{definition}

@@

\begin{notation}
If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
\begin{itemize}
 \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
 \item $c^\infty$ for the infinite word~$c c c\cdots$,
% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
 \item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
\end{itemize}
We also define~${}^{-\infty}c \eqdef (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (^\infty c)^{-1}$.
\end{notation}

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~$^{\pm\infty}c_1\sigma c_2^{\pm\infty}$, where $c_1,c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero), $c_1, c_1^2, c_2, c_2^2\notin I$, and~$\sigma$ is a finite string.
\vincent{We also want $c_1\sigma \notin I$ or $c_1^{-1} \notin I$ depending on what we have...}
In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
\end{definition}

\begin{remark}
 The terminology in the previous definition is borrowed from~\cite{Crawley-Boevey}.
 Note however that our choice of convention differs from \emph{loc. cit.}, resulting in exchanging ``inverse'' and ``direct''.
\end{remark}

\begin{definition}
 A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
 We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
\end{definition}

>>>>

The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
The terminology in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.

\begin{definition}
\label{def:string}
Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
A \defn{finite string} for~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{itemize}
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{itemize}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
For each vertex~$v \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_v$, that starts and ends at~$v$.
%We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
%We usually denote strings by~$\rho, \sigma, \tau$.
%We call \defn{negative simple string} a formal word of length zero of the form $-v$, where $v$ is any vertex of $Q_0$. We denote by
%\(
%\strings^\pm_{\ge -1}(\bar Q) \eqdef \strings^\pm(\bar Q) \sqcup \set{-v}{v \in Q_0}
%\)
%the set of \defn{almost positive unoriented strings}.
%Note that~$\varepsilon_v$ and~$-v$ are different almost positive strings.
%\end{enumerate}
\end{definition}

@@

\begin{notation}
If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
\begin{itemize}
 \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
 \item $c^\infty$ for the infinite word~$c c c\cdots$,
% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
 \item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
\end{itemize}
We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.
\end{notation}

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite chord.
%In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
\end{definition}

\begin{definition}
A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
We denote by~$\strings(\bar Q)$ the set of strings on~$\bar Q$.
We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and we let~$\strings^\pm(\bar Q) \eqdef \set{\{\rho, \rho^{-1}\}}{\rho \in \strings(\bar Q)}$ denote the collection of all \defn{undirected strings} of~$\bar Q$.
\end{definition}
